Determining the alternatives for scalar implicature

### 2016-01-31 Paper/Paper.Rmd
minor
pushing MF changes

$$ p_{S_1}(u \mid m) \propto p_{L_0} (m \mid u)$$

@@

$$p_{S_1}(u \mid m) \propto e^{-\alpha\[-log(p_{L_0}(m \mid u)) - C(u)\]}$$

@@

```{r exp2_altsPlot_likedLoved, fig.pos = "t", fig.align='center', set.cap.width=T, fig.height=2, num.cols.cap=2, fig.cap = "Combined counts for participant-generated alternatives for the "liked \ loved" scale in Experiment 2."}

@@

# Model Comparison

>>>>

$$p_{S_1}(u \mid m) \propto p_{L_0} (m \mid u)$$

@@

$$p_{S_1}(u \mid m) \propto e^{-\alpha[-log(p_{L_0}(m \mid u)) - C(u)]}$$

@@

```{r exp2_altsPlot_likedLoved, fig.pos = "t", fig.align='center', set.cap.width=T, fig.height=2, num.cols.cap=2, fig.cap = "Combined counts for participant-generated alternatives for the 'liked \ loved' scale in Experiment 2."}

@@

# Model

### 2016-01-31 Paper/Paper.tex
pushing MF changes

\begin{abstract}
Successful communication regularly requires listeners to make pragmatic
inferences - enrichments beyond the literal meaning of a speaker's
utterance. For example, when interpreting a sentence such as ``Alice ate
some of the cookies,'' listeners routinely infer that Alice did not eat
all of them. A Gricean account of this phenomena assumes the presence of
alternatives (like ``all of the cookies'') with varying degrees of
informativity, but it remains an open question precisely what these
alternatives are. We use a computational model of pragmatic inference to
test hypotheses about how well different sets of alternatives allow us
to predict scalar implicature performance across a range of different
scales. Our findings suggest that human comprehenders likely consider a
much broader set of alternatives beyond those entailed by the initial
description.

@@

How much of what we mean comes from the words that go unsaid? As
listeners, our ability to make precise inferences about a speaker's
intended meaning in context is an indispensable component of successful
communication. For example, listeners commonly enrich the meaning of the
scalar item \emph{some} to \emph{some but not all} in sentences like
``Alice ate some of the cookies'' (Grice, 1975; Horn, 1984; Levinson,
2000). These inferences, called \emph{scalar implicatures}, have been an
important test case for understanding pragmatic inferences more
generally. A Gricean account of this phenomena assumes listeners reason
about the meaning the speaker intended by incorporating knowledge about
a) alternative scalar items a speaker could have used (such as
\emph{all}) and b) the relative informativity of using such alternatives
(Grice, 1975). According to this account, a listener will infer that the
speaker must have intended that Alice did not eat \emph{all} the cookies
because it would have been underinformative for the speaker to use
\emph{some} when \emph{all} could have been used.

But what are the alternatives that should be considered in this
computation more generally? Under classic accounts of implicature,
listeners consider only those words whose meaning would entail the word
that is actually sent (Horn, 1972), and these alternatives enter into
conventionalized or semi-conventionalized scales (Levinson, 2000). For
example, because \emph{all} entails \emph{some}, and hence is a
``stronger'' meaning, \emph{all} should be considered as an alternative
to \emph{some} in implicatures. Similar scales exist for non-quantifier
scales, e.g. \emph{loved} entails \emph{liked} (and hence ``I liked the
movie'' implicates that I didn't love it).

Recent empirical evidence has called into question whether entailment
scales are all that is necessary for understanding scalar implicature.
For example, Degen \& Tanenhaus (2015) demonstrated that the scalar item
\emph{some} was judged less appropriate when exact numbers were seen as
viable alternatives. And in a different paradigm, Tiel (2014) found
converging evidence that \emph{some} was judged to be atypical for small
quantities. These data provide indirect evidence about a broader set of
alternatives: since \emph{some} is logically true of sets with one or
two members, these authors argued that the presence of salient
alternatives (the words \emph{one} and \emph{two}) reduced the felicity
of \emph{some} via a pragmatic inference.

@@

\[p_{L1}(m \mid u) \propto p_{S_1} (u \mid m) p(m)\]

@@

\[ p_{S_1}(u \mid m) \propto p_{L_0} (m \mid u)\]

@@

\[p_{S_1}(u \mid m) \propto e^{-\alpha(-log(p_{L_0}(m \mid u)) - C(u))}\]

\noindent where \(C(u)\) is the cost of a particular utterance,
\(-log(p_{L_0})\) represents the \emph{surprisal} for the literal
listener (the information content of the utterance), and \(\alpha\) is a
parameter in a standard choice rule. If \(\alpha=0\), speakers choose
randomly and as \(\alpha \rightarrow \infty\), they greedily choose the
highest probability alternative. In our simulations below, we treat
\(\alpha\) as a free parameter and fit it to the data.

To instantiate our signaling game with a tractable message set \(M\), in
our studies we adopt a food-review paradigm: we assume that speakers and
listeners are trying to communicate the number of stars in an online
restaurant review (where \(m \in \{1, 2, 3, 4, 5\}\)). We then use
experiments to measure three components of the model. First, to measure
literal semantics \({p_{L_0} (m \mid u)}\) (we ask experiment
participants to judge whether a message is compatible with a particular
meaning (Experiment 1). Second, to generate a set of plausible
alternative messages in \(U\), we elicit alternatives directly
(Experiment 2). Lastly, to obtain human \(L_1\) pragmatic judgments, we
ask participants to interpret a speaker's utterances (Experiment 3).

@@

Experiment 1 was conducted to approximate literal listener semantic
distributions \(p_{L_0}(m \mid u)\) for five pairs of scalar items taken
from Tiel (2014). We include three conditions in Experiment 1,
corresponding to the sets of alternatives within a scale that
participants were presented with: two-alternatives (``entailment''),
four-alternatives, and five-alternatives. The two-alternatives
entailment condition makes a test of the hypothesis that the two members
of the classic Horn scale (Horn, 1972) are the only alternatives
necessary to predict the strength of listeners' pragmatic inference. The
four- and five-alternatives conditions then add successively more
alternatives to test whether including a larger number of alternatives
will increase model
fit.\footnote{Note that alternatives in the four- and five-alternatives conditions were chosen on the basis of Experiment 2, which was run chronologically after the two-alternative condition; all literal listener experiments are grouped together for simplicity in reporting.}
A secondary goal of Experiments 1a,b,c tests whether the set of
alternatives queried during literal semantic elicitation impacts
compatibility judgments. (If it does we should see differences in
compatibility judgments for shared items between experiments.) We
address this possibility in the results section.

@@

In each condition we recruited 30 participants from Amazon Mechanical
Turk (AMT). In the two-alternative condition, 16 participants were
excluded
\footnote{The majority of respondent data excluded from Experiment 1a was caused by failure to pass training trials. We believe the task may have been too difficult for most respondents and made adjustments to the training trials in Experiments 1b,c}
for either failing to pass two training trails or were not native
English speakers, leaving a total sample of 14 participants. In the
four-alternative condition, 7 participants were excluded for either
failing to pass two training trials or were not native English speakers,
leaving a total sample of 23 participants. In the five-alternative
condition, 3 participants were excluded for either failing to pass two
training trials or were not native English speakers, leaving a total
sample of 27.

@@

The two-alternatives condition included only the scalar pairs from Tiel
(2014). The four-alternatives condition included the two scalar items
plus the top two alternatives generated for each scalar family by
participants in Experiment 2. The five-alternatives condition included
the four previous items plus one more ``neutral'' item chosen from those
alternatives generated in Experiment 2. See Figure
\ref{fig:allScalesTable} for the complete list of alternatives used in
each condition.

@@

Figure \ref{fig:exp2Plots} plots literal listener \(p_{L0}(m|u)\) scalar
item distributions for the three conditions. Each row shows a unique
scalar family with items ordered horizontally by valence. Several trends
are visible. First, in each scale, the alternatives spanned the star
scale, such that there were alternatives that were highly compatible
with both the lowest and highest numbers of stars. Second, there was
clear variability between scalar families. For example, compatibility
judgments for the top items in the \emph{memorable / unforgettable}
scale were more similar than those for \emph{good / excellent} or
\emph{liked / loved.} Finally, there was substantial consistency in
ratings for items that were repeated across experiments, suggesting that
this paradigm elicited stable judgments from participants.

To test our secondary hypothesis, that the different sets of scalar
items queried might result in differences in compatibility judgments
between experiments, we ran a mixed effects model. We regressed
compatibility judgments on scale, number of stars and experiment
(1a,b,c), with subject and word level random effects, which was the
maximal structure that converged. Results indicate no significant
differences between Experiment 1a and 1c, \(b =\)-0.05, \(Z =\) -0.53,
\(p =\) 0.59 or between 1b and 1c, \(b =\) -0.04, \(Z =\) -0.52 \(p =\)
0.6 and the addition of our experiment predictor did not significantly
improve model fit when compared to a model without the experiment
variable using ANOVA \(\chi^2(\) 2 \() =\) 0.43, \(p =\) 0.81.

@@

@@

\caption[Pragmatic listener judgements for our entailment scalar items]{Pragmatic listener judgements for our entailment scalar items. Proportion of participants generating a star rating is shown on the vertical axis, with the horizontal axis showing number of stars on which the utterance was judged. Each line-type shows a different experiment, and colors indicate the stronger (ie excellent) or weaker (ie good) scalar items for each scale. Each panel shows one scalar pair. We are only showing scalar items used for model comparison (items used in Experiments 1a / 3a) for simplicity,}\label{fig:exp2Plots}
\end{figure*}
\end{CodeChunk}

\caption[Combined counts for participant generated alternatives for 'liked  loved' scale from Experiment 2]{Combined counts for participant generated alternatives for 'liked  loved' scale from Experiment 2. Participants were shown a target scalar (either liked or loved) and asked to give three alternatives.}\label{fig:exp2_altsPlot_likedLoved}
\end{figure}
\end{CodeChunk}

@@

Experiment 3 was conducted to measure pragmatic judgments
\(p_{L_1}(m \mid u)\) for five pairs of scalar items taken from Tiel
(2014). We include two conditions in Experiment 3. In the
two-alternatives condition, participants made judgments for items
included in the entailment scales. In the four-alternatives condition,
participants made judgments for the entailment items and also the top
two alternatives elicited for each scale in Experiment 2. Running two
pragmatic judgment conditions allowed us to rule out the potential
effects of having a larger set of alternatives during the pragmatic
judgment elicitation and also provided two sets of human judgments to
compare with model
predictions\footnote{Note that alternatives in the four-alternatives condition were chosen on the basis of Experiment 2, which was run chronologically after the two-alternatives condition; both pragmatic listener experiments are grouped together for simplicity in reporting.}.
A secondary goal of Experiment 3b tests whether the set of alternatives
queried in Experiments 3a,b impacts pragmatic judgments. (If it does we
should see differences in pragmatic judgments between experiments.) We
address this possibility in the results section.

@@

We recruited 100 participants from AMT, 50 for each condition. Data for
9 participants was excluded after participants either failed to pass two
training trials or were non-native English speakers, leaving a total
sample of 41 participants. In the four-alternative condition, data from
7 participants was excluded after participants either failed to pass two
training trials or were not native English speakers, leaving a total
sample of 43 participants.

@@

Figure \ref{fig:exp2Plots} plots pragmatic listener judgments
distributions for ``weak'' / ``strong'' scalar pairs (e.g.
\emph{good}/\emph{excellent}). We only include the original entailment
pairs in this figure for simplicity. Several trends are visible. First,
in each scale participants generated implicatures and were less likely
to assign high star-ratings to weaker scalar terms, despite literal
semantic compatibility. Second, the ``size'' of the difference between
judgments between ``strong'' and ``weak'' scalar items varied by scale,
consistent with results from Tiel (2014).

To test our secondary hypothesis, that the different sets of scalar
items queried might result in differences in pragmatic judgments between
experiments, we ran a mixed effects model. We regressed pragmatic
judgments on scale and experiment (3a,b) with subject and word level
random effects, which was the maximal structure that converged. Results
indicate there were no significant differences between Experiment 3a and
3b, \(b =\) 0.05, \(t(\) 150 \() =\) 1.04, \(p =\) 0.3 and the addition
of our experiment predictor did not significantly improve model fit when
compared to a model without the experiment variable using ANOVA
\(\chi^2(\) 1 \() =\) 1.13, \(p =\) 0.29.

\section{Model Results}\label{model-results}

Using literal semantic data from Experiments 1a,b,c we conducted three
simulations with our model. Each simulation used the specific literal
semantic data to specify the scale representation available to our
model.

@@

\caption[Model fit]{Model fit: model predictions are plotted on the x-axis. Human judgments from Exerpiment 3b are plotted on the y-axis. Coloration denotes star rating for which judgment was made.}\label{fig:fiveAltsScatter}
\end{figure*}
\end{CodeChunk}

@@

By varying the type of scale representations available to our Bayesian
model we investigated the effects of alternatives on scalar implicature.
Model fit with human judgments was significantly improved by the
inclusion of alternatives beyond the typical ``strong'' and ``weak''
scalar items. The two-alternatives model contained only entailment
items, which, under classic accounts, should be sufficient to generate
implicature. Model performance with this limited alternative set was
poor when compared to human judgments from Experiment 3a,b (row 1, Table
\ref{xtable}). Building off findings in Franke (2014), in which the
best-fitting model assigned substantial weight to \emph{none} as an
alternative, we included a ``generic'' negative alternative that was
only compatible with 1-star. Model fit for this modified entailment
alternative set did improve, however overall correlation was still low
(row 2, Table \ref{xtable}). Model fit jumped substantially by adding
the top-two alternatives for each scale (row 3, Table \ref{xtable}).
Finally, our five-alternatives model included a neutral alternative
along with the original entailment pair and top two (row 4, Table
\ref{xtable}).

While model improvement seemed to be related to the number of
alternatives present, we did not see substantial differences between our
four- and five-alternative models. One possibility is that alternatives
are differentially salient in context. Our current framework makes the
simplifying assumption that all alternatives are equally salient.
However, it may well be the case that while both \emph{all} and
\emph{most} are \emph{present} during pragmatic enrichment of
\emph{some}, \emph{all} is more salient and therefore should carry
greater weight in our model. Findings from Experiment 2, in which
participants generated plausible alternatives, support this intuition,
as some alternatives appeared more often than others. This distinction
between binary \emph{presence} and graded \emph{salience} is an
important one that deserves further investigation.

It is also likely that the precise set of alternatives present during
implicature are domain dependent. Our current empirical paradigm
elicited literal semantics, pragmatic judgments and plausible
alternatives all within the restricted domain of restaurant reviews.
Participant data may have differed greatly if we had instead asked them
to respond in a movie review paradigm, which would have been acceptable
for a number of our stimuli (e.g. \emph{memorable}/\emph{unforgettable},
\emph{liked}/\emph{loved}, etc.).

Considering the possibility that alternative sets may be domain specific
even for scalar items may provide a way forward in uniting generalized
and particularized implicatures. Findings from our investigation
indicate that human literal semantic and pragmatic judgments are often
graded and diverse, much like the set of plausible alternatives that
give rise to pragmatic inferences.

@@

Thanks to NSF BCS. Thanks to Michael Franke, Judith Degen, and Noah
Goodman.

@@

>>>>

\begin{abstract}
Successful communication regularly requires listeners to make pragmatic
inferences - enrichments beyond the literal meaning of a speaker's
utterance. For example, when interpreting a sentence such as ``Alice ate
some of the cookies,'' listeners routinely infer that Alice did not eat
all of them. A Gricean account of this phenomena assumes the presence of
alternatives (like ``all of the cookies'') with varying degrees of
informativity, but it remains an open question precisely what these
alternatives are. We collect empirical measurements of speaker and
listener judgments and use these as inputs to a computational model of
pragmatic inference. This approach allows us to test hypotheses about
how well different sets of alternatives predict implicature performance
across a range of different scales. Our findings suggest that
comprehenders likely consider a much broader set of alternatives beyond
those entailed by the initial description.

@@

How much of what we mean comes from the words that go unsaid? As
listeners, our ability to make precise inferences about a speaker's
intended meaning in context is indispensable to successful
communication. For example, listeners commonly enrich the meaning of the
scalar item \emph{some} to \emph{some but not all} in sentences like
``Alice ate some of the cookies'' (Grice, 1975; Horn, 1984; Levinson,
2000). These inferences, called \emph{scalar implicatures}, have been an
important test case for understanding pragmatic inferences more
generally. A Gricean account of this phenomenon assumes listeners reason
about the meaning the speaker intended by incorporating knowledge about
a) alternative scalar items a speaker could have used (such as
\emph{all}) and b) the relative informativity of using such alternatives
(Grice, 1975). According to this account, a listener will infer that the
speaker must have intended that Alice did not eat all the cookies
because otherwise it would have been underinformative to use the
descriptor \emph{some} when the alternative \emph{all} could have been
used just as easily.

But what are the alternatives that should be considered in the
implicature computation more generally? Under classic accounts,
listeners consider only those words whose meanings entail the actual
message (Horn, 1972), and these alternatives enter into conventionalized
or semi-conventionalized scales (Levinson, 2000). For example, because
\emph{all} entails \emph{some}, and hence is a ``stronger'' meaning,
\emph{all} should be considered as an alternative to \emph{some} in
implicatures. Similar scales exist for non-quantifier scales, e.g.
\emph{loved} entails \emph{liked} (and hence ``I liked the movie''
implicates that I didn't love it).

Recent empirical evidence has called into question whether entailment
scales are all that is necessary for understanding scalar implicature.
For example, Degen \& Tanenhaus (2015) demonstrated that the scalar item
\emph{some} was judged less appropriate when exact numbers were seen as
viable alternatives. And in a different paradigm, Tiel (2014) found
converging evidence that \emph{some} was judged to be atypical for small
quantities. These data provide indirect evidence about a broader set of
alternatives: since \emph{some} is logically true of sets with one or
two members, these authors argued that the presence of salient
alternatives (the words \emph{one} and \emph{two}, for example) reduced
the felicity of \emph{some} via a pragmatic inference.

@@

\[p_{L_1}(m \mid u) \propto p_{S_1} (u \mid m) p(m) \label{eq:rsa}\]

@@

\[p_{S_1}(u \mid m) \propto p_{L_0} (m \mid u)\]

@@

\[p_{S_1}(u \mid m) \propto e^{-\alpha[-log(p_{L_0}(m \mid u)) - C(u)]}\]

\noindent where \(C(u)\) is the cost of a particular utterance,
\(-log(p_{L_0})\) represents the \emph{surprisal} of the message for the
literal listener (the information content of the utterance), and
\(\alpha\) is a parameter in a standard choice rule. If \(\alpha=0\),
speakers choose randomly and as \(\alpha \rightarrow \infty\), they
greedily choose the highest probability alternative. In our simulations
below, we treat \(\alpha\) as a free parameter and fit it to the data.

To instantiate our signaling game with a tractable message set \(M\), in
our studies we adopt the world of restaurant reviews as our
communication game. We assume that speakers and listeners are trying to
communicate the number of stars in an online restaurant review (where
\(m \in \{1, 2, 3, 4, 5\}\)). We then use experiments to measure three
components of the model. First, to measure literal semantics
\({p_{L_0} (m \mid u)}\) (we ask experiment participants to judge
whether a message is compatible with a particular meaning (Experiment
1). Second, to generate a set of plausible alternative messages in
\(U\), we elicit alternatives directly (Experiment 2). Lastly, to obtain
human \(L_1\) pragmatic judgments, we ask participants to interpret a
speaker's utterances (Experiment 3).

@@

Experiment 1 was conducted to approximate literal listener semantic
distributions \(p_{L_0}(m \mid u)\) for five pairs of scalar items taken
from Tiel (2014). We include three conditions in Experiment 1,
corresponding to the sets of alternatives within a scale that
participants were presented with: two alternatives (``entailment''),
four alternatives, and five alternatives. The two alternatives condition
makes a test of the hypothesis that the two members of the classic Horn
(entailment) scale (Horn, 1972) are the only alternatives necessary to
predict the strength of listeners' pragmatic inference. The four and
five alternatives conditions then add successively more alternatives to
test whether including a larger number of alternatives will increase
model
fit.\footnote{Note that alternatives in the four and five alternatives conditions were chosen on the basis of Experiment 2, which was run chronologically after the two-alternative condition; all literal listener experiments are grouped together for simplicity in reporting.}
A secondary goal of Experiment 1 is to test whether the set of
alternatives queried during literal semantic elicitation impacts
compatibility judgments. (If it does we should see differences in
compatibility judgments for shared items between experiments.)

@@

Conditions were run sequentially. In each condition we recruited 30
participants from Amazon Mechanical Turk (AMT). In the two alternative
condition, 16 participants were excluded for either failing to pass two
training trails or were not native English speakers, leaving a total
sample of 14
participants.\footnote{The majority of respondent data excluded from the two alternative condition was caused by failure to pass training trials. We believe the task may have been too difficult for most respondents and made adjustments to the training trials in later conditions.}
In the four alternative condition, 7 participants were excluded for
either failing to pass two training trials or were not native English
speakers, leaving a total sample of 23 participants. In the five
alternative condition, 3 participants were excluded for either failing
to pass two training trials or were not native English speakers, leaving
a total sample of 27.

@@

The two alternatives condition included only the scalar pairs from Tiel
(2014). The four alternatives condition included the two scalar items
plus the top two alternatives generated for each scalar family by
participants in Experiment 2. The five alternatives condition included
the four previous items plus one more neutral item chosen from those
alternatives generated in Experiment 2. See Figure
\ref{fig:allScalesTable} for the complete list of alternatives used in
each condition.

@@

Figure \ref{fig:exp2Plots} plots literal listener \(p_{L0}(m|u)\) scalar
item distributions for the three conditions. Each row shows a unique
scalar family with items ordered horizontally by valence. Several trends
are visible. First, in each scale, the alternatives spanned the star
scale, such that there were alternatives that were highly compatible
with both the lowest and highest numbers of stars. Second, there was
clear variability between scalar families. For example, compatibility
judgments for the top items in the \emph{memorable / unforgettable}
scale were more similar than those for \emph{good / excellent} or
\emph{liked / loved}. Finally, there was substantial consistency in
ratings for items that were repeated across experiments, suggesting that
this paradigm elicited stable judgments from participants.

To test our secondary hypothesis, that the different sets of scalar
items might result in differences in compatibility judgments between
experiments, we ran a mixed effects model. We regressed compatibility
judgments on scale, number of stars and condition, with subject and word
level random effects, which was the maximal structure that converged.
Results indicate no significant differences between Experiment 1a and
1c, \(b =\)-0.05, \(Z =\) -0.53, \(p =\) 0.59 or between 1b and 1c,
\(b =\) -0.04, \(Z =\) -0.52 \(p =\) 0.6 and the addition of condition
as a predictor did not significantly improve model fit when compared to
a model without the experiment variable using ANOVA \(\chi^2(\) 2
\() =\) 0.43, \(p =\) 0.81.

@@

\caption[Combined counts for participant-generated alternatives for the 'liked  loved' scale in Experiment 2]{Combined counts for participant-generated alternatives for the 'liked  loved' scale in Experiment 2.}\label{fig:exp2_altsPlot_likedLoved}
\end{figure}
\end{CodeChunk}

@@

\caption[Pragmatic listener judgements for scalar items]{Pragmatic listener judgements for scalar items. Proportion of participants generating a star rating is shown on the vertical axis, with the horizontal axis showing number of stars on which the utterance was judged. Line type denotes condition, and colors indicate the particular scalar items. Each panel shows one scalar pair, with only entailment items (two alternatives condition) shown here for simplicity.}\label{fig:exp2Plots}
\end{figure*}
\end{CodeChunk}

@@

Experiment 3 was conducted to measure pragmatic
judgments---\(p_{L_1}(m \mid u)\) in Equation \ref{eq:rsa}. As in
Experiment 1, we include several conditions to test inferences in the
presence of different alternative sets. In the two alternatives
condition, participants made judgments for items included in the
entailment scales. In the four alternatives condition, participants made
judgments for the entailment items and also the top two alternatives
elicited for each scale in Experiment 2. Including two conditions with
differing alternatives allowed us to rule out the potential effects of
having a larger set of alternatives during the pragmatic judgment
elicitation and also provided two sets of human judgments to compare
with model
predictions.\footnote{Note that alternatives in the four alternatives condition were chosen on the basis of Experiment 2, which was run chronologically after the two alternatives condition; both pragmatic listener experiments are grouped together for simplicity in reporting.}

@@

We recruited 100 participants from AMT, 50 for each condition. Data for
9 participants was excluded from the two alternatives condition after
participants either failed to pass two training trials or were
non-native English speakers, leaving a total sample of 41 participants.
In the four alternative condition, data from 7 participants was excluded
after participants either failed to pass two training trials or were not
native English speakers, leaving 43 participants.

@@

Figure \ref{fig:exp2Plots} plots pragmatic listener judgments
distributions for ``weak'' / ``strong'' scalar pairs (e.g.
\emph{good}/\emph{excellent}). We include only the original entailment
pairs in this figure for simplicity. Several trends are visible. First,
in each scale participants generated implicatures. They were
substantially less likely to assign high star ratings to weaker scalar
terms, despite the literal semantic compatibility of those terms with
those states shown in Experiment 1. Second, the size of the difference
between strong and weak scalar items varied considerably across scales,
consistent with previous work (Tiel, 2014).

To test our secondary hypothesis, that the different sets of scalar
items in the two conditions might result in differences in pragmatic
judgments for the same items, we fit a mixed effects model. We regressed
pragmatic judgments on scale and condition with subject- and word-level
random effects, which was the maximal structure that converged. There
were no significant differences between conditions, \(b =\) 0.05, \(t(\)
150 \() =\) 1.04, \(p =\) 0.3 and the addition of the condition
predictor did not significantly improve model fit when compared to a
model without that variable \(\chi^2(\) 1 \() =\) 1.13, \(p =\) 0.29.

\section{Model}\label{model}

Using literal listener data from Experiment 1, we conducted a set of
simulations with the RSA model. Each simulation kept the model constant,
fitting the choice parameter \(\alpha\) as a free parameter, but used a
set of alternatives to specify the scale over which predictions were
computed. We considered four different alternative sets, with empirical
measurements corresponding to those shown in Table
\textbackslash{}ref\{fig:allScalesTable): 1) the two alternatives in the
classic entailment scales, 2) those two alternatives with the addition
of a generic negative alternative, 3) the expanded set of four
alternatives tested in Experiment 1, and 4) the expanded set of five
alternatives tested in Experiment 1.

Model fit with human judgments was significantly improved by the
inclusion of alternatives beyond the entailment items (Table
\ref{fig:xtable}). The two alternatives model contained only entailment
items, which, under classic accounts, should be sufficient to generate
implicature, but fit to data was quite poor with these items. The
addition of a generic negative element produced some gains in
performance, but much higher performance was found when we included four
and five alternatives, with the alternatives derived empirically for the
specific scale we used. An example fit for the five-alternative model is
shown in Figure \ref{fig:fiveAltsScatter}.

@@

\caption[Judgments from Experiment 3, four alternatives condition, are plotted against model predictions]{Judgments from Experiment 3, four alternatives condition, are plotted against model predictions. Colors show the star rating for individual judgments.}\label{fig:fiveAltsScatter}
\end{figure*}
\end{CodeChunk}

@@

Pragmatic inference requires reasoning about alternatives. The
fundamental pragmatic computation is counterfactual: ``if she had meant
X, she would have said Y, but she didn't.'' Yet the nature of these
alternatives has been controversial. For a few well-studied scales, a
small set of logically-determined alternatives has been claimed to be
all that is necessary (Horn, 1972). For other, contextually-determined
inferences, the issue of alternatives has been considered relatively
intractable in terms of formal inquiry (Sperber \& Wilson, 1995).

In our current work, we used the rational speech act framework to
investigate the set of alternatives that best allowed the model to
predict pragmatic judgments across a series of different scales. We
found that the best predictions came when a range of scale-dependent
negative and neutral alternatives were added to the implicature
computation, suggesting the importance of considering non-entailment
alternatives. This work builds on previous investigations, reinforcing
the claim that negative alternatives are critical for understanding
implicature (Franke, 2014), and replicates and extends findings that
different lexical scales produce strikingly different patterns of
inference ({\textbf{???}}).

While improvements in model fit were substantial as we moved from two to
four alternatives, we saw only a minor increase in fit from the move to
five alternatives. One possible explanation is that alternatives are
differentially salient in context, and moving to larger sets would
consider weighting the alternatives differentially (as Franke, 2014
did). Preliminary simulations using weightings derived from Experiment 2
provide some support for this idea but would require further empirical
work for confirmation.

The precise set of alternatives present during implicature is likely to
be domain dependent. Our current empirical paradigm elicited literal
semantics, pragmatic judgments, and plausible alternatives all within
the restricted domain of restaurant reviews. Our measurements might have
differed substantially if we had instead grounded our ratings in a
different context. Future investigations should probe the
context-specificity of the weight and availability of particular
alternative sets.

More broadly, considering the context- and domain-specificity of
alternative sets may provide a way to unite what Grice (1975) called
``generalized'' (cross-context) and ``particularized''
(context-dependent) implicatures. Rather than being grounded in a firm
distinction, we may find that these categories are simply a reflection
of the effects of context on a constantly-shifting set of pragmatic
alternatives.

@@

Thanks to NSF BCS \#1456077 for support, and thanks to Michael Franke,
Judith Degen, and Noah Goodman for valuable discussion.

@@

Sperber, D., \& Wilson, D. (1995). \emph{Relevance: Communication and
cognition} (2nd ed.). Oxford, UK: Blackwell.
